[Standartox](http://standartox.uni-landau.de)

### 2019-10-14 talk/talk43.Rmd

```{r setup, echo=FALSE, include=FALSE, warning=FALSE, message=FALSE}
src = '/home/scharmueller/Projects/etox-base/R'
source(file.path(src, 'gn_setup.R'))
```

@@

### Andreas Scharmüller<br>
### Verena C. Schreiner<br>
### Ralf B. Schäfer
<br><br>
### Quantitative Landscape Ecology<br/>
### iES Landau, Institute for Environmental Sciences<br>
### University Koblenz-Landau
<br>
<img src="https://www.uni-koblenz-landau.de/de/landau/fb7/umweltwissenschaften/logos/land-ecol-neu.jpg" width="100">
<img src="https://www.uni-koblenz-landau.de/de/uni/organisation/verwaltung/abteilungen/abt-1/dokumente-ab1/uni-logo-farbig.jpg" width="200">

@@

Bernhardt et al. 2017
<img src="/home/scharmueller/Projects/etox-base/talk/data/bernhardt_et_al_chem.png" width="300px">

@@

---
background-image: url(/home/scharmueller/Projects/etox-base/talk/data/stream.jpg)
background-size: 400px
background-position: 90% 50%

@@

--
<img src="/home/scharmueller/Projects/etox-base/talk/data/epa_ecotox_screenshot.png" width="800px">

@@

<img src="/home/scharmueller/Projects/etox-base/talk/data/epa_ecotox_screenshot.png" width="500px">

@@

<img src="/home/scharmueller/Projects/etox-base/talk/data/organigram2.png" width="950px" style="position:absolute; left:10px; top:130px;">

@@

--
<img src="/home/scharmueller/Projects/etox-base/talk/data/standartox_screenshot.png" width="800px">

@@

.pull-left[
<img src="/home/scharmueller/Projects/etox-base/talk/data/standartox_screenshot.png" width="500px">
### Aim: Prepare ecotoxicological test data in a __reproducible__ and __standardized__ way
]

@@

standartox(cas = '52-68-6',
           endpoint = 'EC50',
           effect = 'MOR',
           duration = c(48, 96),
           taxon = 'Oncorhynchus mykiss')
```

@@

<img src="/home/scharmueller/Projects/etox-base/talk/data/logos/worms.png" width="250px" style="position:absolute; bottom:30px; left:260px;">

<img src="/home/scharmueller/Projects/etox-base/talk/data/logos/chebi.png" width="250px" style="position:absolute; bottom:140px; right:110px;">

<img src="/home/scharmueller/Projects/etox-base/talk/data/logos/pubchem.png" width="250px" style="position:absolute; bottom:25px; right:90px;">

>>>>

```{r setup, echo=FALSE, include=FALSE, warning=FALSE, message=FALSE}
src = '/home/scharmueller/Projects/standartox-build/R'
source(file.path(src, 'gn_setup.R'))
```

@@

### Andreas Scharmüller<br>
### Verena C. Schreiner<br>
### Ralf B. Schäfer
<br><br>
### Quantitative Landscape Ecology<br/>
### iES Landau, Institute for Environmental Sciences<br>
### University Koblenz-Landau
<br>
<img src="https://www.uni-koblenz-landau.de/de/landau/fb7/umweltwissenschaften/logos/land-ecol-neu.jpg" width="100">
<img src="https://www.uni-koblenz-landau.de/de/uni/organisation/verwaltung/abteilungen/abt-1/dokumente-ab1/uni-logo-farbig.jpg" width="200">
<img src="https://www.uni-koblenz-landau.de/de/uni/organisation/verwaltung/abteilungen/abt-1/dokumente-ab1/uni-logo-farbig.jpg" width="200">
<img src="https://de.wikipedia.org/wiki/Universit%C3%A4t_Stra%C3%9Fburg#/media/Datei:Universit%C3%A9_de_Strasbourg.svg" width="100">

@@

Bernhardt et al. 2017
<img src="/home/scharmueller/Projects/standartox-build/talk/data/bernhardt_et_al_chem.png" width="300px">

@@

---
background-image: url(/home/scharmueller/Projects/standartox-build/talk/data/stream.jpg)
background-size: 400px
background-position: 90% 50%

@@

--
<img src="/home/scharmueller/Projects/standartox-build/talk/data/epa_ecotox_screenshot.png" width="800px">

@@

<img src="/home/scharmueller/Projects/standartox-build/talk/data/epa_ecotox_screenshot.png" width="500px">

@@

<img src="/home/scharmueller/Projects/standartox-build/talk/data/organigram2.png" width="950px" style="position:absolute; left:10px; top:130px;">

@@

--
<img src="/home/scharmueller/Projects/standartox-build/talk/data/standartox_screenshot.png" width="800px">

@@

.pull-left[
<img src="/home/scharmueller/Projects/standartox-build/talk/data/standartox_screenshot.png" width="500px">
### Aim: Prepare ecotoxicological test data in a __reproducible__ and __standardized__ way
]

@@

stx_query(cas = '52-68-6',
          endpoint = 'EC50',
          effect = 'MOR',
          duration = c(48, 96),
          taxon = 'Oncorhynchus mykiss')
```

@@

<img src="/home/scharmueller/Projects/standartox-build/talk/data/logos/worms.png" width="250px" style="position:absolute; bottom:30px; left:260px;">

<img src="/home/scharmueller/Projects/standartox-build/talk/data/logos/chebi.png" width="250px" style="position:absolute; bottom:140px; right:110px;">

<img src="/home/scharmueller/Projects/standartox-build/talk/data/logos/pubchem.png" width="250px" style="position:absolute; bottom:25px; right:90px;">
